Literature Review - Informal

### 2019-12-23 Literature Review/Literature Review - Informal/sample.tex
added comments

\begin{itemize} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
Coded \end{itemize}

@@

\fr{What are the standard techniques used in swarms? that is, how are swarms and their interactions modelled? how are solutions computed? what kind of algorithms are used in this area? most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}

@@

\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as
expected by the user.

@@

\end{itemize}

@@

\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
  SREs which have a limited or erroneous model.

\item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}

@@

\begin{itemize} 
	\item Verification of goal achievement under different payoffs: can we ensure that
	self-interested agents will, in fact, show cooperative emergent properties? A similar question
	arises in terms of valuations (how much cost each agent incurs). 
	\item A priori consideration of
	reliability: Can we learn and take into account the fact that robots may fail throughout the
	progress of a mission when we assign tasks? 
\end{itemize}

@@

\begin{itemize} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
the stability of the learning process. However, the particular problem I suggest is to consider the
modelling in a decentralised manner and with the consideration of evolving numbers of agents in
teams. \end{itemize}

@@

As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
The methods which I feel may be applicable are  \begin{itemize} \item Alternating Maximisation: This
is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
order to make this work, we would also need to consider how to select the feature space of sub-trees
and how to collect this information. \end{itemize}

@@

\begin{itemize}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{itemize}

@@

\begin{itemize}
	\item The agents act in a deterministic environment. This suggests that predicted futures will
	be close enough to the ground truth.
	\item The agents are uncoupled from one another. This is a strong assumption to make and
	essentially allows us to consider the agents as completely independent of one another. 
	\item The agents can easily communicate with one another. This allows for longer pieces of
	communication (most often predicted trajectories) to be communicated between agents.
\end{itemize}

@@

\begin{itemize}
	\item Significant exploration is required with regards to the optimisation problem. Especially
	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
	approximate methods (such as sampling) should be explored and their effect on the system
	guarantees presented.
	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
	determine the uncertainty in the environment model in order to generate control laws. We should
	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
	particle filters, against modern deep learning methods for propagation.
	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
	together whilst maintaining a specified distance from one another). Consider, then, the case
	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
	and hence requires adaptation. It would again be interesting to consider the use of neural
	networks in this manner. However, specifically we should consider whether the use of a function
	approximator in the form of an NN might result in a violation of the constraints.
	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
	effect that each agent has on the other, the effect of the environment on all agents, estimating the
	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
	here that I believe game-theoretic notions (especially differential games) will come to our
	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
	in the case of multiple disturbances, but I will elaborate on this in the applied problems
	section.
\end{itemize}

@@

\begin{itemize}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
	\item Modular Robotics?
\end{itemize}

@@

@@

@@

\begin{itemize}
	\item Each agent $i$ takes into consideration their observations of the past N measurements of the
	actions selected by another agent $j$. Using this, a Gaussian Process (GP) regression informs the
	distribution of the action that will likely be selected by $j$, effectively performing a
	one-step lookahead of $j$'s actions. By propagating the effects of this predicted input $i$ can
	then determine a likely trajectory for $j$ and then perform its own update accordingly. Whilst
	this may seem computationally expensive, its advantage lies in the fact that it requires little
	communication across the agents. An immediate disadvantage of this is that, as the number of
	agents increases, $i$ would need to perform all of these calculations for each $j \neq i$. I'm
	not yet confident on the feasibility or the usefulness of this technique, but looking further
	into the literature (which seems to add new things every day) may provide insights which could
	help refine the technique. This method is, in many ways, similar to that presented in 
	\cite{Conte2014} and \cite{Dai2017}. The advantage of this proposal over that in 
	\cite{Conte2014} is that it does not assume that the uncertainties from the predictions of other
	agents are bounded. Likewise, the advantage over \cite{Dai2017} is that our proposal allows for
	all systems to update at each time step.

	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
	public belief based on the observed actions of all agents. This joint belief will likely provide
	some representation of the trajectories that each agent will carry out or an understanding of
	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
	will be chosen from a family of existing models using a recursive Bayesian update. The idea
	would be for this update to be conditioned on the history of observations as is done in 
	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
	state and use this, in combination with their own system models to determine a feasible
	trajectory. The challenge here would be proving the stability and controllability of the system
	and that it requires communication with a central controller. However, it would appear to be a
	feasible area of exploration.
\end{itemize}

@@

Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
when considering its application in stochastic environments. In particular, the ideas presented
below concern the transport problem of swarms, i.e. moving a swarm from an initial distribution to a
desired distribution.

\begin{itemize}
	\item Consideration of state constraints or boundary conditions (terms which I will use
interchangeably) in the diffusion process. In general, stochastic swarm systems are modelled using a
particular stochastic difference equation (the Ito equation). However, this does not account for any
boundary conditions on the diffusion. Indeed most swarms use simple 'stop-and-turn' notions of
obstacle avoidance. However, in environments where there are human operators, or in general areas
where we do not want swarms to enter, it is important to have a guarantee of constraint
satisfaction. To accomplish this, I propose extending the Ito equation to incorporate boundary
conditions. This will, firstly, provide a more suitable model for the evolution of a swarm system in
confined spaces, allowing for a more intuitive understanding of the future behaviour of the swarm.
Furthermore, it may present an opportunity for us to consider the decentralised control of the
agents which can ensure state constraint satisfaction. The resources which are most relevant to this
study (and from which the ideas are derived) are
\cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.

@@

\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
number of their nearest neighbours. However, this may not always be the case. It will often be that
in different environmental conditions, the observation or communication capabilities of the robots
may increase or decrease. To better accomodate for this fact, I propose the extension of the model
with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
way into swarm dynamics. It will, however, become particularly important in cases where we can no
longer take the consistency of agent communication for granted. 
\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
not seem like the connection of MJD and swarm dynamics has been made yet.
\end{itemize}

@@

\begin{itemize}
	\item Stable exploration in MARL. This builds on the ideas of \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective} and
	an important point mentioned in \cite{Marinescu2014} that 'the dynamics implied by multi-agent
	systems lead to stochastic behaviour resulting sometimes in undesired effects'. In particular,
	most RL methods require some trade-off between exploration and exploitation. It is, therefore,
	required that we determine a safe manner in which MARL agents may explore without leading to
	unstable behaviour. This would require extending the work of \cite{Berkenkamp2017} and/or 
	\cite{Jin2018Stability-certifiedPerspective} to the multi-agent case. Note that 
	\cite{Jin2018Stability-certifiedPerspective} does actually consider a multi-agent case, but with
	independent learners who do not consider the effect that they have on the other agent(s). The
	particular extension that I propose is to consider the coupled effect between agents as part of
	the determination of a safe set for exploration.

	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
	problems. Although it makes strong assumptions about the nature of the system, in practice it
	has shown strong results. Particular examples of this are found in 
	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
	systems by considering sub-groups within the population. Each of these may be updated
	individually. It would be interesting to examine how this might increase the complexity, and
	also the generalisability of the mean-field method.
	\item A Dynamical Systems analysis on Games. The ideas here still require further reading on my
	part but the potential directions are largely summarised in Section 2.3.1.
\end{itemize}

>>>>

\begin{enumerate} \item Swarms \item Multi Agent Reinforcement Learning (MARL) \item Decentralised
Partially Observed Markov Decision Processes (Dec-POMDP) \item Game Theoretic Approaches \item Hard
Coded \end{enumerate}

@@

\fr{What are the standard techniques used in swarms? that is, how are swarms and their interactions modelled? how are solutions computed? what kind of algorithms are used in this area? most importantly, does any of these overlap with any of the areas below, for example (PO)MDPs?}

@@

\begin{enumerate} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as
expected by the user.

@@

\end{enumerate}

@@

\begin{enumerate} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
  SREs which have a limited or erroneous model.

\item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{enumerate}

@@

\begin{enumerate} 
	\item Verification of goal achievement under different payoffs: can we ensure that
	self-interested agents will, in fact, show cooperative emergent properties? A similar question
	arises in terms of valuations (how much cost each agent incurs). 
	\item A priori consideration of
	reliability: Can we learn and take into account the fact that robots may fail throughout the
	progress of a mission when we assign tasks? 
\end{enumerate}

@@

\begin{enumerate} \item Modelling evolving teammates: The purpose of this is to more strictly ensure
the stability of the learning process. However, the particular problem I suggest is to consider the
modelling in a decentralised manner and with the consideration of evolving numbers of agents in
teams. \end{enumerate}

@@

As Dec-POMDPs are the theoretical formulation of MARL problems, it stands to reason that other
methods for solving Dec-POMDPs should provide insights into improving MARL. Fortunately Oliehock in
\cite{OliehoekDecentralizedPOMDPs} presents a number of existing methods towards solving Dec-POMDPs.
The methods which I feel may be applicable are  \begin{enumerate} \item Alternating Maximisation: This
is effectively coordinate ascent for determining a joint policy. \item Approximation as Bayesian
Games: Perhaps solving the repeated Bayesian Game through MARL would be more efficient. It does,
however, force us to ask how best to sub-divide a Dec-POMDP into a series of Bayesian Games  \item
Selecting sub-tree policies: Could DL be used to determine which sub-tree policies are optimal? In
order to make this work, we would also need to consider how to select the feature space of sub-trees
and how to collect this information. \end{enumerate}

@@

\begin{enumerate}
	\item The arbitrary form of the feedback control laws
	\item The non-convexity and intractability of the chance constraints
	\item The complexity of the uncertainty propagations
	\item Establishing stability of the control problem
\end{enumerate}

@@

\begin{enumerate}
	\item The agents act in a deterministic environment. This suggests that predicted futures will
	be close enough to the ground truth.
	\item The agents are uncoupled from one another. This is a strong assumption to make and
	essentially allows us to consider the agents as completely independent of one another. 
	\item The agents can easily communicate with one another. This allows for longer pieces of
	communication (most often predicted trajectories) to be communicated between agents.
\end{enumerate}

@@

\begin{enumerate}
	\item Significant exploration is required with regards to the optimisation problem. Especially
	for non-linear (or coupled systems), solving the optimisation problem is a struggle. As such,
	approximate methods (such as sampling) should be explored and their effect on the system
	guarantees presented.
	\item Uncertainty propagation in SMPC is also an important problem since we must be able to
	determine the uncertainty in the environment model in order to generate control laws. We should
	consider a comparison of formal techniques, such as Bayesian inference (e.g. Markov models) or
	particle filters, against modern deep learning methods for propagation.
	\item Adaptive MPC is particularly important when considering failures in a system. In his talk,
	Mark Cannon considers the platooning problem (in which multiple autonomous vehicles move
	together whilst maintaining a specified distance from one another). Consider, then, the case
	where one vehicle undergoes a fault (burst tyre etc). The system model must incorporate this,
	and hence requires adaptation. It would again be interesting to consider the use of neural
	networks in this manner. However, specifically we should consider whether the use of a function
	approximator in the form of an NN might result in a violation of the constraints.
	\item Distributed predictive control. This is what, in my view, we could work towards. This is a
	difficult problem due to the coupled nature of the system dynamics. We will need to consider: the
	effect that each agent has on the other, the effect of the environment on all agents, estimating the
	future behaviour of each agent, and ensuring that all agents do not violate the constraints. It is
	here that I believe game-theoretic notions (especially differential games) will come to our
	aid. Similarly, mean-field games should be considered in the general N-agent problem, as well as
	in the case of multiple disturbances, but I will elaborate on this in the applied problems
	section.
\end{enumerate}

@@

\begin{enumerate}
	\item Mean-field predictive control. Consider the case of a hybrid system, in which many components
	interact with each other. In addition, we may consider that there are multiple known disturbances
	acting on the system. This, at first seems like an impossible problem to solve due to the many
	interactions between all elements of the system. However, we can consider this as a game
	theoretic problem in which the components and the disturbances are players. The relatively new
	class of 'mean-field games' is a method which allows the many body problem to be approximated as
	a series of two-agent problems \cite{Yang2018}. Whilst the concerns in the 'Distributed
	predictive control' remain, this may prove to be a valuable area of applied research.
	\item Swarm control. Swarms often have simpler control rules implemented within each agent,
	which emerge into more complex results. It would be interesting to consider the application of
	robust and stochastic MPC with the aim of improving swarm results and satisfying constraints of
	the emergent phenomenon. This would be of particular interest in the case where the swarm has to
	track multiple objectives. A prediction of the swarm evolution may prove beneficial to ensure
	that all agents comply with the expected behaviour as the swarm switches tasks. Similarly, an
	adaptive stochastic model would be interesting to examine here to remain robust to agent
	failures in the group.
	\item Modular Robotics?
\end{enumerate}

\fr{All the above looks interesting. However, we need to understand
  how much the scalability issue is going to affect the strength of
  the results we can expect. Is a multi-agent extension of MPC
  completely hopeless? or can we find ``islands of tractability'',
  perhaps in combination with some of the other methods that you
  mention?}

@@

\fr{The above sounds a bit technical, but the interest for MARL is apparent. It might be worth to understand what are the limits of applicability of these resutls, that is, what assumptions are they based on.}

@@

\fr{I agree that we first need to understand what is exactly meant by
  stabililty across all these different works, and possibly use a
  notion that is relevant and interesting, especially in a multi-agent
  contex as you point you hereafter.}

@@

\begin{enumerate}
	\item Each agent $i$ takes into consideration their
          observations of the past N measurements of the actions
          selected by another agent $j$. Using this, a Gaussian
          Process (GP) regression informs the distribution of the
          action that will likely be selected by $j$, effectively
          performing a one-step lookahead of $j$'s actions. By
          propagating the effects of this predicted input $i$ can then
          determine a likely trajectory for $j$ and then perform its
          own update accordingly. Whilst this may seem computationally
          expensive, its advantage lies in the fact that it requires
          little communication across the agents. An immediate
          disadvantage of this is that, as the number of agents
          increases, $i$ would need to perform all of these
          calculations for each $j \neq i$. I'm not yet confident on
          the feasibility or the usefulness of this technique, but
          looking further into the literature (which seems to add new
          things every day) may provide insights which could help
          refine the technique. This method is, in many ways, similar
          to that presented in \cite{Conte2014} and
          \cite{Dai2017}. The advantage of this proposal over that in
          \cite{Conte2014} is that it does not assume that the
          uncertainties from the predictions of other agents are
          bounded. Likewise, the advantage over \cite{Dai2017} is that
          our proposal allows for all systems to update at each time
          step.

          \fr{It sounds interesting, might warrant further
            investigation.}

	\item The second proposal is motivated by the ideas presented in \cite{Foerster} and 
	\cite{Heirung2019}. In this methodology, a centralised controller maintains and updates a joint
	public belief based on the observed actions of all agents. This joint belief will likely provide
	some representation of the trajectories that each agent will carry out or an understanding of
	the other agents' future actions. In a similar manner to \cite{Heirung2019}, this joint belief
	will be chosen from a family of existing models using a recursive Bayesian update. The idea
	would be for this update to be conditioned on the history of observations as is done in 
	\cite{Wingate2012}, though this is more flexible. Agents have access to this joint public belief
	state and use this, in combination with their own system models to determine a feasible
	trajectory. The challenge here would be proving the stability and controllability of the system
	and that it requires communication with a central controller. However, it would appear to be a
	feasible area of exploration.
\end{enumerate}

@@

Swarm systems and algorithms are a relatively mature area of research. Yet there is work to be done
when considering its application in stochastic environments. In particular, the ideas presented
below concern the transport problem of swarms, i.e., moving a swarm from an initial distribution to a
desired distribution.

\begin{enumerate}
	\item Consideration of state constraints or boundary
          conditions (terms which I will use interchangeably) in the
          diffusion process. In general, stochastic swarm systems are
          modelled using a particular stochastic difference equation
          (the Ito equation). However, this does not account for any
          boundary conditions on the diffusion. Indeed most swarms use
          simple 'stop-and-turn' notions of obstacle
          avoidance. However, in environments where there are human
          operators, or in general areas where we do not want swarms
          to enter, it is important to have a guarantee of constraint
          satisfaction. To accomplish this, I propose extending the
          Ito equation to incorporate boundary conditions. This will,
          firstly, provide a more suitable model for the evolution of
          a swarm system in confined spaces, allowing for a more
          intuitive understanding of the future behaviour of the
          swarm.  Furthermore, it may present an opportunity for us to
          consider the decentralised control of the agents which can
          ensure state constraint satisfaction. The resources which
          are most relevant to this study (and from which the ideas
          are derived) are
          \cite{Inoue2019,Sartoretti2014,Shahrokhi2019,Li2017}.

          \fr{I have basic knowledge of Ito equation from unrelated past experience and must say that it is not trivial to work with them.}

@@

\item Finally, all of the diffusive methods for swarms consider a time invariant network topology.
By this, I mean that it is assumed that each agent can communicate with, or observe, a certain
number of their nearest neighbours. However, this may not always be the case. It will often be that
in different environmental conditions, the observation or communication capabilities of the robots
may increase or decrease. To better accomodate for this fact, I propose the extension of the model
with the addition of Markovian Jump Dynamics (MJD). MJD allows us to take into account discrete
'jumps' in the structure of the system model which occur randomly. It has shown a large degree of
success in stochastic control of multi-agent systems but has, as far as I can see, yet to find its
way into swarm dynamics. It will, however, become particularly important in cases where we can no
longer take the consistency of agent communication for granted. 
\cite{FUHRMANFrancescoRUSSO,Ma2017,Li2017} have begun to make progress in these areas, but it does
not seem like the connection of MJD and swarm dynamics has been made yet.
\end{enumerate}

\fr{Please refer also to the items in my email.}

@@

\begin{enumerate}
	\item Stable exploration in MARL. This builds on the ideas of
          \cite{Berkenkamp2017,Jin2018Stability-certifiedPerspective}
          and an important point mentioned in \cite{Marinescu2014}
          that 'the dynamics implied by multi-agent systems lead to
          stochastic behaviour resulting sometimes in undesired
          effects'. In particular, most RL methods require some
          trade-off between exploration and exploitation. It is,
          therefore, required that we determine a safe manner in which
          MARL agents may explore without leading to unstable
          behaviour. This would require extending the work of
          \cite{Berkenkamp2017} and/or
          \cite{Jin2018Stability-certifiedPerspective} to the
          multi-agent case. Note that
          \cite{Jin2018Stability-certifiedPerspective} does actually
          consider a multi-agent case, but with independent learners
          who do not consider the effect that they have on the other
          agent(s). The particular extension that I propose is to
          consider the coupled effect between agents as part of the
          determination of a safe set for exploration.

        \fr{That's interesting. Can we leverage on results in Model
          Predictive Control?}

	\item Improvement of mean-field MARL. This method has shown the most promise for large scale
	multi agent systems since it allows us to reduce a many-body problem to a series of two-body
	problems. Although it makes strong assumptions about the nature of the system, in practice it
	has shown strong results. Particular examples of this are found in 
	\cite{Subramanian2019,Yang2018}. I am not yet sure about how to expand upon these methods but
	perhaps a way to start would be to consider the expansion of mean-field methods to heterogeneous
	systems by considering sub-groups within the population. Each of these may be updated
	individually. It would be interesting to examine how this might increase the complexity, and
	also the generalisability of the mean-field method.
	\item A Dynamical Systems analysis on Games. The ideas here
          still require further reading on my part but the potential
          directions are largely summarised in Section 2.3.1.

          \fr{Interesting direction, but in my opinion the game-theoretic analysis should be grounded in some already well-developed theory (MPC?)}
\end{enumerate}
